\documentclass{ltxdoc}
%\GetFileInfo{\jobname.sty}
\def\fileversion{4.1.0}
\def\filedate{May 29, 2014}
\usepackage{lmodern}
\usepackage[numbered]{hypdoc}
\usepackage{hologo}
\usepackage{hyperref, xcolor}
\definecolor{myblue}{rgb}{0.22,0.45,0.70}% light blue
\hypersetup{colorlinks=true, linkcolor=myblue, urlcolor=myblue, hyperindex}
\usepackage{longtable, booktabs}
\usepackage{tikz}
\usepackage{xparse, ifthen}
\usepackage{fontawesome}
\EnableCrossrefs
\CodelineIndex
\RecordChanges

\begin{document}
\title{The \textsf{fontawesome} package\\High quality web icons}
\author{%
  Xavier Danaux\thanks{E-mail: \href{mailto:xdanaux@gmail.com}{\tt xdanaux@gmail.com}} (Original \hologo{LaTeX} code)\\%
  Nazar Gerasymchuk\thanks{Github: \href{https://github.com/Troyane}{\tt Troyane}} (New \hologo{LaTeX} code)\\%
  Geoffrey Gouez\thanks{Github: \href{https://github.com/Cicatrice}{\tt Cicatrice}} (New \hologo{LaTeX} code)\\%
  Dave Gandy (font and icons design)}
\date{Version \fileversion, released on \filedate}
\maketitle

\begin{abstract}
The \textsf{fontawesome} package grants access to 439 web-related icons provided by the included \emph{Font Awesome} free font, designed by Dave Gandy and released\footnote{See \url{http://fortawesome.github.com/Font-Awesome} for more details about the font itself} under the open SIL Open Font License\footnote{Available at \url{http://scripts.sil.org/OFL}.}.

This package requires the \textsf{fontspec} package and either the \hologo{Xe}\hologo{(La)TeX} or Lua\hologo{(La)TeX} engine to load the included otf font.
\end{abstract}
\def\currentversion{4.1}
\changes{v4.1.0} {2014/05/29}{Update to match Font Awesome version 4.1.0. New code generation.}
\changes{v3.1.1} {2013/05/10}{Update to match Font Awesome version 3.1.1, with 53 new icons.}
\changes{v3.0.2-1}{2013/03/23}{Bigfix release: corrected the swap of the \cs{text-height} and \cs{text-width} icons.}
\changes{v3.0.2} {2013/03/21}{First public release (version number set to match the included FontAwesome.otf font version).}
\makeatletter
\let\PrintMacroName@original\PrintMacroName
%\let\PrintDescribeMacro\@gobble
%\let\PrintDescribeEnv\@gobble
\let\PrintMacroName\@gobble
%\let\PrintEnvName\@gobble
\begin{macro}{\faTextHeight}
\changes{v3.0.2-1}{2013/03/23}{Corrected binding.}
\end{macro}
\begin{macro}{\faTextWidth}
\changes{v3.0.2-1}{2013/03/23}{Corrected binding.}
\end{macro}
\let\PrintMacroName\PrintMacroName@original
\makeatother

\bigskip

\section{Introduction}
%The \textsf{\jobname} package aims to enable easy access in \hologo{(La)TeX} to high quality icons covering
%\hyperref[section:web_application]{web application},
%\hyperref[section:text_editor]{text editor},
%\hyperref[section:directional]{directional},
%\hyperref[section:video_player]{video player},
%\hyperref[section:social]{social} and
%\hyperref[section:medical]{medical}
%pictograms.
It is a redistribution of the free (as in beer) \emph{Font Awesome} otf font with specific bindings for \hologo{(La)TeX}.

\section{Requirements}
The \textsf{fontawsome} package requires the \textsf{fontspec} package and either the \hologo{Xe}\hologo{(La)TeX} or Lua\hologo{(La)TeX} engine to load the included otf font.

\section{Usage}
\DescribeMacro{\faicon}
Once the \textsf{fontawesome} package loaded, icons can be accessed through the general \cs{faicon}, which takes as mandatory argument the \meta{name} of the desired icon, or through a direct command specific to each icon. The full list of icon designs, names and direct commands are showcased next.

\newenvironment{showcase}%
  {%
% \begin{longtable}{ccp{3cm}p{3.5cm}p{1cm}}% debug: shows icons with both generic and specific commands
   \begin{longtable}{cp{5cm}p{5cm}p{3cm}}
   \cmidrule[\heavyrulewidth]{1-3}% \toprule
% \bfseries Icon& \bfseries Icon& \bfseries Name& \bfseries Direct command& \\% debug
   \bfseries Icon& \bfseries Name& \bfseries Direct command& \\
   \cmidrule{1-3}\endhead}
  {\cmidrule[\heavyrulewidth]{1-3}% \bottomrule
   \end{longtable}}
\NewDocumentCommand{\showcaseicon}{mmg}{%
% \faicon{#1}& \csname#2\endcsname& \itshape #1& \ttfamily \textbackslash #2\index{\ttfamily \textbackslash #2}& \IfNoValueTF{#3}{}{\tag{#3}}\\}% debug
  \faicon{#1}& \itshape #1& \ttfamily \textbackslash #2\index{\ttfamily \textbackslash #2}& \IfNoValueTF{#3}{}{\tag{#3}}\\}
\newcommand{\tag}[1]{{%
  \small\sffamily%
  \ifthenelse{\equal{#1}{\currentversion}}{%
    \tikz[baseline={(TAG.base)}]{
      \node[white, fill=myblue, rounded corners=3pt, inner sep=1.5pt] (TAG) {New in \currentversion\vphantom{Ay!}};
    }}{
	\ifthenelse{\equal{#1}{gone}}{%
    		\tikz[baseline={(TAG.base)}]{
      		\node[black!50, fill=black!25, rounded corners=3pt, inner sep=1.5pt] (TAG) {gone (?)\vphantom{Ay!}};
    }}	{
  		\ifthenelse{\equal{#1}{alias}}{%
    			\textcolor{black!50}{(alias)}}{
    				\tikz[baseline={(TAG.base)}]{
      				\node[white, fill=black!65, rounded corners=3pt, inner sep=1.5pt] (TAG) {Since #1\vphantom{Ay!}};
				}}%
		}%
	}%
  }}

\include{fontawesome-doc-symbols}

\PrintChanges
\PrintIndex
\end{document}
